### 2022-07-19 sections/conferences-full.tex
Update conferences-full.tex

\begin{benumerate}{72}

%% \item{González-Bustamante, B., \& Aguilar, D. (2022). {\itshape Territorial Patterns in Digital Development and Open Government: Evidence from Chilean Local Governments}. Presentation delivered at the International Political Science Association Seminar Smart Cities and Open Government: Local Responses to Participation, Public Information, and Democracy, Madrid.}\vspace{1mm}

>>>>

\begin{benumerate}{74}

\item{González-Bustamante, B., \& Aguilar, D. (2022). {\itshape Digital Development and Open Government: Evidence from Chilean Local Governments}. Presentation delivered at the Digital Democracy Workshop, Digital Society Initiative, University of Zurich, Zurich.}\vspace{1mm}

\item{González-Bustamante, B., \& Aguilar, D. (2022). {\itshape Territorial Patterns in Digital Development and Open Government: Evidence from Chilean Local Governments}. Presentation delivered at the International Political Science Association Seminar Smart Cities and Open Government: Local Responses to Participation, Public Information, and Democracy, Madrid.}\vspace{1mm}
